### 2015-06-11 rapport/msp.tex
rapport_11_06

After these over-constraints are applied, $\Gamma_{hybrid}$ is a MSP DAG. As a result, the binary tree decomposition algorithm of Valdes \& Al can be applied on $\Gamma_{hybrid}$. However, because of updated-computations inserted in $\Gamma_{data}$, we have to define additional reduction rules for the algorithm. %For an updated-computation $c^*_j(c_j,\text{update}(\{w_i\text{, }\forall i\text{ }c_i \prec c_j\}))$, we define $*_j$ as the update needed by $c_j$, $*_j = \text{update}(\{w_i\text{, }\forall i\text{ }c_i \prec c_j\})$. As a result, the updated-computation $c^*_j$ is defined by $c^*_j(c_j,*_j)$. 
The initial label of the edges of the graph $L^{-1}(\Gamma_{hybrid})$ to reduce are the computations of the multi-stencil program. Four new rules are needed to perform the binary tree decomposition of $\Gamma_{hybrid}$ and are defined in Figure~\ref{fig:newrules}. The symetric transforations are not represented.

  \path[->]
    (x) edge node [above] {$c_1^*$} (y)
    (y) edge node [above] {$c_2$} (z);
  \end{tikzpicture}
  }
\hspace{50pt}
%ARROW
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
%TRANSFORMATION
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
   \node[] (s1) at (1.5,0.5) {$\mathcal{S}$};
   \node[] (s2) at (1,1.5) {$\mathcal{S}$};
   \node[] (star) at (0.5,2.5) {$*_1$};
   \node[] (t1) at (1.5,2.5) {$c_1$};
   \node[] (t2) at (2,1.5) {$c_2$};

  \path[->]
    (x) edge node {} (y)
    (s1) edge node {} (s2)
        edge node {} (t2)
    (s2) edge node {} (star)
         edge node {} (t1);
  \end{tikzpicture}
}
\\
%SECOND RULE
%FIRST RULE
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (z) at (3,0) {};

  \path[->]
    (x) edge node [above] {$c_1^*$} (y)
    (y) edge node [above] {$c_2^*$} (z);
  \end{tikzpicture}
  }
\hspace{50pt}
%ARROW
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
%TRANSFORMATION
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
   \node[] (s1) at (1.5,0.5) {$\mathcal{S}$};
   \node[] (s2) at (0.5,1.5) {$\mathcal{S}$};
   \node[] (s3) at (2.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (0,2.5) {$*_1$};
   \node[] (t1) at (1,2.5) {$c_1$};
   \node[] (star2) at (2,2.5) {$*_2$};
   \node[] (t2) at (3,2.5) {$c_2$};

  \path[->]
    (x) edge node {} (y)
    (s1) edge node {} (s2)
        edge node {} (s3)
    (s2) edge node {} (star1)
         edge node {} (t1)
    (s3) edge node {} (star2)
         edge node {} (t2);
  \end{tikzpicture}
}
\\
%THIRD RULE
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};

  \path[->]
    (x) edge [bend left] node [above] {$c_1^*$} (y)
        edge [bend right] node [below] {$c_2$} (y);
  \end{tikzpicture}
  }
\hspace{50pt}
%ARROW
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
%TRANSFORMATION
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
   \node[] (p) at (1.5,0.5) {$\mathcal{P}$};
   \node[] (s) at (1,1.5) {$\mathcal{S}$};
   \node[] (star) at (0.5,2.5) {$*_1$};
   \node[] (t1) at (1.5,2.5) {$c_1$};
   \node[] (t2) at (2,1.5) {$c_2$};

  \path[->]
    (x) edge node {} (y)
    (p) edge node {} (s)
        edge node {} (t2)
    (s) edge node {} (star)
        edge node {} (t1);
  \end{tikzpicture}
}
\\
%FOURTH RULE
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};

  \path[->]
    (x) edge [bend left] node [above] {$c_1^*$} (y)
        edge [bend right] node [below] {$c_2^*$} (y);
  \end{tikzpicture}
  }
\hspace{50pt}
%ARROW
\subfloat[]{
$\Rightarrow$
}
\hspace{50pt}
%TRANSFORMATION
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
   \node[] (p) at (1.5,0.5) {$\mathcal{P}$};
   \node[] (s2) at (0.5,1.5) {$\mathcal{S}$};
   \node[] (s3) at (2.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (0,2.5) {$*_1$};
   \node[] (t1) at (1,2.5) {$c_1$};
   \node[] (star2) at (2,2.5) {$*_2$};
   \node[] (t2) at (3,2.5) {$c_2$};

  \path[->]
    (x) edge node {} (y)
    (p) edge node {} (s2)
        edge node {} (s3)
    (s2) edge node {} (star1)
         edge node {} (t1)
    (s3) edge node {} (star2)
         edge node {} (t2);
  \end{tikzpicture}
}
\caption{Reduction rules of the decomposition tree algorithm.}
\label{fig:newrules}
\end{center}
\end{figure}

Using those additional reduction rules, the binary series-parallel tree decomposition can be computed in linear time. A complete example of reduction is given in Figure~\ref{fig:example}. The initial $\Gamma_{hybrid}$ DAG and its inverse line graph are given first, followed by the set of reductions. The label of the final single edge corresponds to the binary tree decomposition of the initial $\Gamma_{hybrid}$ graph.

@@

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (7,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

@@

   %reduction c2 c4
   \node[] (s6) at (3.5,1) {$\mathcal{S}$};
   \node[] (c2) at (3,2) {$c_2$};
   \node[] (s7) at (4,2) {$\mathcal{S}$};
   \node[] (star4) at (3.5,3) {$*_4$};
   \node[] (c4) at (4.5,3) {$c_4$};

@@

@@

    %reduction c7 c8
    (s6) edge node {} (c2)
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\end{center}
\caption{Big example}
\label{fig:example}
\end{figure}

@@

   %reduction c2 c6
   \node[] (s8) at (3.5,1) {$\mathcal{S}$};
   \node[] (c6) at (4,2) {$c_6$};
   \node[] (s6) at (3,2) {$\mathcal{S}$};
   \node[] (c2) at (2.5,3) {$c_2$};
   \node[] (s7) at (3.5,3) {$\mathcal{S}$};
   \node[] (star4) at (3,4) {$*_4$};
   \node[] (c4) at (4,4) {$c_4$};

@@

    %reduction c2 c6
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (8,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (7,0.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,1.5) {$c_7$};
   \node[] (s4) at (7.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (7,2.5) {$*_8$};
   \node[] (c8) at (8,2.5) {$c_8$};

   %reduction c2 c4 c6 c3 c5
   \node[] (p1) at (4,0.5) {$\mathcal{P}$};
   \node[] (s5) at (3,1) {$\mathcal{S}$};
   \node[] (c3) at (2.5,2) {$c_3$};
   \node[] (c5) at (3.5,2) {$c_5$};
   \node[] (s8) at (5,1) {$\mathcal{S}$};
   \node[] (c6) at (5.5,2) {$c_6$};
   \node[] (s6) at (4.5,2) {$\mathcal{S}$};
   \node[] (c2) at (4,3) {$c_2$};
   \node[] (s7) at (5,3) {$\mathcal{S}$};
   \node[] (star4) at (4.5,4) {$*_4$};
   \node[] (c4) at (5.5,4) {$c_4$};

@@

    %reduction c2 c4 c6 c3 c5
    (p1) edge node {} (s5)
         edge node {} (s8)
    (s5) edge node {} (c3)
         edge node {} (c5)
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (8,0) {};

>>>>

After these over-constraints are applied, $\Gamma_{hybrid}$ is a MSP DAG. As a result, the binary tree decomposition algorithm of Valdes \& Al can be applied on $\Gamma_{hybrid}$. However, because of updated-computations inserted in $\Gamma_{data}$, we have to define additional reduction rules for the algorithm. %For an updated-computation $c^*_j(c_j,\text{update}(\{w_i\text{, }\forall i\text{ }c_i \prec c_j\}))$, we define $*_j$ as the update needed by $c_j$, $*_j = \text{update}(\{w_i\text{, }\forall i\text{ }c_i \prec c_j\})$. As a result, the updated-computation $c^*_j$ is defined by $c^*_j(c_j,*_j)$. 
The initial label of the edges of the graph $L^{-1}(\Gamma_{hybrid})$ to reduce are the computations of the multi-stencil program. %Four new rules are needed to perform the binary tree decomposition of $\Gamma_{hybrid}$ and are defined in Figure~\ref{fig:newrules}. The symetric transforations are not represented.

% \begin{figure}[h!]
% \captionsetup[subfigure]{labelformat=empty}
% \begin{center}
% %FIRST RULE
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (z) at (3,0) {};

%   \path[->]
%     (x) edge node [above] {$c_1^*$} (y)
%     (y) edge node [above] {$c_2$} (z);
%   \end{tikzpicture}
%   }
% \hspace{50pt}
% %ARROW
% \subfloat[]{
% $\Rightarrow$
% }
% \hspace{50pt}
% %TRANSFORMATION
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
%    \node[] (s1) at (1.5,0.5) {$\mathcal{S}$};
%    \node[] (s2) at (1,1.5) {$\mathcal{S}$};
%    \node[] (star) at (0.5,2.5) {$*_1$};
%    \node[] (t1) at (1.5,2.5) {$c_1$};
%    \node[] (t2) at (2,1.5) {$c_2$};

%   \path[->]
%     (x) edge node {} (y)
%     (s1) edge node {} (s2)
%         edge node {} (t2)
%     (s2) edge node {} (star)
%          edge node {} (t1);
%   \end{tikzpicture}
% }
% \\
% %SECOND RULE
% %FIRST RULE
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (z) at (3,0) {};

%   \path[->]
%     (x) edge node [above] {$c_1^*$} (y)
%     (y) edge node [above] {$c_2^*$} (z);
%   \end{tikzpicture}
%   }
% \hspace{50pt}
% %ARROW
% \subfloat[]{
% $\Rightarrow$
% }
% \hspace{50pt}
% %TRANSFORMATION
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
%    \node[] (s1) at (1.5,0.5) {$\mathcal{S}$};
%    \node[] (s2) at (0.5,1.5) {$\mathcal{S}$};
%    \node[] (s3) at (2.5,1.5) {$\mathcal{S}$};
%    \node[] (star1) at (0,2.5) {$*_1$};
%    \node[] (t1) at (1,2.5) {$c_1$};
%    \node[] (star2) at (2,2.5) {$*_2$};
%    \node[] (t2) at (3,2.5) {$c_2$};

%   \path[->]
%     (x) edge node {} (y)
%     (s1) edge node {} (s2)
%         edge node {} (s3)
%     (s2) edge node {} (star1)
%          edge node {} (t1)
%     (s3) edge node {} (star2)
%          edge node {} (t2);
%   \end{tikzpicture}
% }
% \\
% %THIRD RULE
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};

%   \path[->]
%     (x) edge [bend left] node [above] {$c_1^*$} (y)
%         edge [bend right] node [below] {$c_2$} (y);
%   \end{tikzpicture}
%   }
% \hspace{50pt}
% %ARROW
% \subfloat[]{
% $\Rightarrow$
% }
% \hspace{50pt}
% %TRANSFORMATION
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
%    \node[] (p) at (1.5,0.5) {$\mathcal{P}$};
%    \node[] (s) at (1,1.5) {$\mathcal{S}$};
%    \node[] (star) at (0.5,2.5) {$*_1$};
%    \node[] (t1) at (1.5,2.5) {$c_1$};
%    \node[] (t2) at (2,1.5) {$c_2$};

%   \path[->]
%     (x) edge node {} (y)
%     (p) edge node {} (s)
%         edge node {} (t2)
%     (s) edge node {} (star)
%         edge node {} (t1);
%   \end{tikzpicture}
% }
% \\
% %FOURTH RULE
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (1.5,0) {};

%   \path[->]
%     (x) edge [bend left] node [above] {$c_1^*$} (y)
%         edge [bend right] node [below] {$c_2^*$} (y);
%   \end{tikzpicture}
%   }
% \hspace{50pt}
% %ARROW
% \subfloat[]{
% $\Rightarrow$
% }
% \hspace{50pt}
% %TRANSFORMATION
% \subfloat[]{
% \begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
%    \node[circle,draw=black,fill=black,scale=0.3] (x) at (0,0) {};
%    \node[circle,draw=black,fill=black,scale=0.3] (y) at (3,0) {};
%    \node[] (p) at (1.5,0.5) {$\mathcal{P}$};
%    \node[] (s2) at (0.5,1.5) {$\mathcal{S}$};
%    \node[] (s3) at (2.5,1.5) {$\mathcal{S}$};
%    \node[] (star1) at (0,2.5) {$*_1$};
%    \node[] (t1) at (1,2.5) {$c_1$};
%    \node[] (star2) at (2,2.5) {$*_2$};
%    \node[] (t2) at (3,2.5) {$c_2$};

%   \path[->]
%     (x) edge node {} (y)
%     (p) edge node {} (s2)
%         edge node {} (s3)
%     (s2) edge node {} (star1)
%          edge node {} (t1)
%     (s3) edge node {} (star2)
%          edge node {} (t2);
%   \end{tikzpicture}
% }
% \caption{Reduction rules of the decomposition tree algorithm.}
% \label{fig:newrules}
% \end{center}
% \end{figure}

% Using those additional reduction rules, the binary series-parallel tree decomposition can be computed in linear time. 
A complete example of reduction is given in Figure~\ref{fig:example}. The initial $\Gamma_{hybrid}$ DAG and its inverse line graph are given first, followed by the set of reductions. The label of the final single edge corresponds to the binary tree decomposition of the initial $\Gamma_{hybrid}$ graph.

@@

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   %\node[] (c8) at (6.5,1.5) {$c_8^*$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
        edge node {} (s2)
    (s2) edge node {} (star1)
        edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8);
        edge node {} (s4)
    (s4) edge node {} (star8)
        edge node {} (c8);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c4d) at (4,0.5) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (5,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (7,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (6,0.5) {$\mathcal{S}$};
   \node[] (c7) at (5.5,1.5) {$c_7$};
   %\node[] (c8) at (6.5,1.5) {$c_8^*$};
   \node[] (s4) at (6.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (6,2.5) {$*_8$};
   \node[] (c8) at (7,2.5) {$c_8$};

@@

   %reduction c2 c4
   \node[] (s6) at (3.5,1) {$\mathcal{S}$};
   \node[] (c2) at (3,2) {$c_2$};
   %\node[] (c4) at (4,2) {$c_4^*$};
   \node[] (s7) at (4,2) {$\mathcal{S}$};
   \node[] (star4) at (3.5,3) {$*_4$};
   \node[] (c4) at (4.5,3) {$c_4$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8)

@@

    %reduction c7 c8
    (s6) edge node {} (c2)
    %     edge node {} (c4);
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\end{center}
\caption{Big example}
\label{fig:example}
\end{figure}

@@

   %reduction c2 c6
   \node[] (s8) at (3.5,1) {$\mathcal{S}$};
   \node[] (c6) at (4,2) {$c_6$};
   \node[] (s6) at (3,2) {$\mathcal{S}$};
   \node[] (c2) at (2.5,3) {$c_2$};
   %\node[] (c4) at (3.5,3) {$c_4^*$};
   \node[] (s7) at (3.5,3) {$\mathcal{S}$};
   \node[] (star4) at (3,4) {$*_4$};
   \node[] (c4) at (4,4) {$c_4$};

@@

    %reduction c2 c6
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
    %     edge node {} (c4);
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c1d) at (2,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c6d) at (6,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (8,0) {};

   %reduction c0 c1
   \node[] (s1) at (1,0.5) {$\mathcal{S}$};
   \node[] (c0) at (0.5,1.5) {$c_0$};
   %\node[] (c1) at (1.5,1.5) {$c_1^*$};
   \node[] (s2) at (1.5,1.5) {$\mathcal{S}$};
   \node[] (star1) at (1,2.5) {$*_1$};
   \node[] (c1) at (2,2.5) {$c_1$};

   %reduction c7 c8
   \node[] (s3) at (7,0.5) {$\mathcal{S}$};
   \node[] (c7) at (6.5,1.5) {$c_7$};
   %\node[] (c8) at (7.5,1.5) {$c_8^*$};
   \node[] (s4) at (7.5,1.5) {$\mathcal{S}$};
   \node[] (star8) at (7,2.5) {$*_8$};
   \node[] (c8) at (8,2.5) {$c_8$};

   %reduction c2 c4 c6 c3 c5
   \node[] (p1) at (4,0.5) {$\mathcal{P}$};
   \node[] (s5) at (3,1) {$\mathcal{S}$};
   \node[] (c3) at (2.5,2) {$c_3$};
   \node[] (c5) at (3.5,2) {$c_5$};
   \node[] (s8) at (5,1) {$\mathcal{S}$};
   \node[] (c6) at (5.5,2) {$c_6$};
   \node[] (s6) at (4.5,2) {$\mathcal{S}$};
   \node[] (c2) at (4,3) {$c_2$};
   %\node[] (c4) at (5,3) {$c_4^*$};
   \node[] (s7) at (5,3) {$\mathcal{S}$};
   \node[] (star4) at (4.5,4) {$*_4$};
   \node[] (c4) at (5.5,4) {$c_4$};

@@

    %reduction c0 c1
    (s1) edge node {} (c0)
    %     edge node {} (c1)
         edge node {} (s2)
    (s2) edge node {} (star1)
         edge node {} (c1)
    %reduction c7 c8
    (s3) edge node {} (c7)
    %     edge node {} (c8)
         edge node {} (s4)
    (s4) edge node {} (star8)
         edge node {} (c8)

    %reduction c2 c4 c6 c3 c5
    (p1) edge node {} (s5)
         edge node {} (s8)
    (s5) edge node {} (c3)
         edge node {} (c5)
    (s8) edge node {} (s6)
         edge node {} (c6)
    (s6) edge node {} (c2)
         %edge node {} (c4);
         edge node {} (s7)
    (s7) edge node {} (star4)
         edge node {} (c4);
  \end{tikzpicture}
}
\\
\subfloat[]{
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[circle,draw=black,fill=black,scale=0.3] (c0s) at (0,0) {};
   \node[circle,draw=black,fill=black,scale=0.3] (c8d) at (8,0) {};
